Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-07 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following \TODO{replace $\alpha$ by $\alpha'$}: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta^3_p},\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=m_1}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m_2}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j$

------------------------

$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
$\\

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^{1b}_p}},  
				{{\Post^{1b}_p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred^1_p \iff {\Pred^{1a}_p}
		\land {\Pred^{1b}_p}\land \alpha^1_p=\beta^1_{pj_0}$, $\Post^1_p={\Post^{1a}_p}\uplus 
		{\Post^{1b}_p}$ where ${{\Post^{1b}_p}}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^{2a}},  
				{\Post^{2a}}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^{2b}},  
				{\Post^{2b}}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha^2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred^{2a}}
		\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0}$, $\Post^2={\Post^{2a}}\uplus 
		{\Post^{2b}}$ where ${\Post^{2b}}$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^{2a}},  
				{\Post^{2a}}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
\\
\Pred\,'=\big(\bigwedge_{i=0}^{m_1}
{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land \\
~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
\Post'=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
$

Concerning $Q$, we consider only the paths for which it moves. So for all states for which we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^{2b}},  
				{\Post^{2b}}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha^2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha^3_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
				{{\Post_p^b}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
\Post_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\

We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}$

Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0.. \alpha'_n]}$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.

>>>>

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha'}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
\Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {\Pred''_{1p}},  
				{\Post''_{1p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred_{1p} \iff {\Pred'_{1p}}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}$, $\Post_{1p}={\Post'_{1p}}\uplus 
		{\Post''_{1p}}$ where ${{\Post''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred_2 \iff {\Pred'_2}
		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

Concerning $Q$, we consider only the paths for which it moves. So for all states for which we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n_k\!-\!1)] Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {{\Pred''_2}},  
				{{\Post''_2}}}
				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k\!+\!1)..(n_k'\!-\!1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=0}^{(n_k-1)}\!\!\Post''_{1j}}}$\\
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$, 
$\forall j \in  (J\cap\Holes(Q)),\,$\\
$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=0}^{n_k-1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
\Pred_k=\bigwedge_{i=0}^{n_k-1}\!\!\Pred''_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred''_2 \subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0.. \alpha'_n]}$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.
